---
title: "Sick and Inactive Days varying by State"
author: "Drew Chung"
date: "12/7/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initial Setup
I first needed to read in the data using readstata13 and read.dta13. Then I seperated the data into separate subsets catgorized by the states. 
```{r, warning=FALSE, message=FALSE}
library(readstata13)
adult_morbidity <- read.dta13("adults_morbidity_03.dta")

Guerrero <- subset(adult_morbidity, state == "12")
Hidalgo <- subset(adult_morbidity, state == "13")
Michoaca <- subset(adult_morbidity, state == "16")
Puebla <- subset(adult_morbidity, state == "21")
Queretar <- subset(adult_morbidity, state == "22")
San_Luis <- subset(adult_morbidity, state == "24")
Veracruz <- subset(adult_morbidity, state == "30")
```

## Mexico Map Package
There is a github package online that is used for Mexico's map. It is very useful for our specific analysis. In order to use this package, we first need to set a few things up:
```{r, warning=FALSE,message=FALSE}
if (!require("remotes")) {
  install.packages("remotes")
}
remotes::install_github("diegovalle/mxmaps")
library("mxmaps")
if (!require("choroplethr")) {
  install.packages("choroplethr")
}
```

## Average sick and inactive days
We calculate the overall average amount of sick days and inactive days in our entire dataframe first. This is so we can compare this number to each state later on. 

```{r}
mean(adult_morbidity$days_sick, na.rm = T)
mean(adult_morbidity$days_inactivity, na.rm = T)
```

## Creating our Maps
This paper only uses data from 7 states. We will show you first the map of the entire country to show you which states are involved in the project and which states are not. Then we will show a second map that features only the maps that are involved in the project so it is easier to see and compare the means. 

## Average Sick Days

```{r}
df_mxstate$meansickdays <- rep(NA)
df_mxstate[[12,"meansickdays"]] <- mean(Guerrero$days_sick, na.rm = T)
df_mxstate[[13,"meansickdays"]] <- mean(Hidalgo$days_sick, na.rm = T)
df_mxstate[[16,"meansickdays"]] <- mean(Michoaca$days_sick, na.rm = T)
df_mxstate[[21,"meansickdays"]] <- mean(Puebla$days_sick, na.rm = T)
df_mxstate[[22,"meansickdays"]] <- mean(Queretar$days_sick, na.rm = T)
df_mxstate[[24,"meansickdays"]] <- mean(San_Luis$days_sick, na.rm = T)
df_mxstate[[30,"meansickdays"]] <- mean(Veracruz$days_sick, na.rm = T)

df_mxstate$value <- df_mxstate$meansickdays
mxstate_choropleth(df_mxstate,
                   num_colors = 1,
                   title = "Average Sick Days (Entire Country)")
df_mxstate$value <- df_mxstate$meansickdays
mxstate_choropleth(df_mxstate,
                   zoom = subset(df_mxstate, state_name %in% c("Guerrero", "Hidalgo", "Michoacán", "Puebla", "Querétaro", "San Luis Potosí", "Veracruz"))$region,
                   num_colors = 7,
                   title = "Average Sick Days (Only the States in the Project)")
```

## Average Inactive Days
```{r}
df_mxstate$meaninactivedays <- rep(NA)
df_mxstate[[12,"meaninactivedays"]] <- mean(Guerrero$days_inactivity, na.rm = T)
df_mxstate[[13,"meaninactivedays"]] <- mean(Hidalgo$days_inactivity, na.rm = T)
df_mxstate[[16,"meaninactivedays"]] <- mean(Michoaca$days_inactivity, na.rm = T)
df_mxstate[[21,"meaninactivedays"]] <- mean(Puebla$days_inactivity, na.rm = T)
df_mxstate[[22,"meaninactivedays"]] <- mean(Queretar$days_inactivity, na.rm = T)
df_mxstate[[24,"meaninactivedays"]] <- mean(San_Luis$days_inactivity, na.rm = T)
df_mxstate[[30,"meaninactivedays"]] <- mean(Veracruz$days_inactivity, na.rm = T)

df_mxstate$value <- df_mxstate$meaninactivedays
mxstate_choropleth(df_mxstate,
                   num_colors = 1,
                   title = "Average Inactive Days (Entire Country)")
df_mxstate$value <- df_mxstate$meaninactivedays
mxstate_choropleth(df_mxstate,
                   zoom = subset(df_mxstate, state_name %in% c("Guerrero", "Hidalgo", "Michoacán", "Puebla", "Querétaro", "San Luis Potosí", "Veracruz"))$region,
                   num_colors = 7,
                   title = "Average Inactive Days (Only the States in the Project)")
```

## Impact of cash-transfer program subject to different States

```{r}
df_mxstate$coefficient <- rep(NA)
df_mxstate[[12,"coefficient"]] <- 0
df_mxstate[[13,"coefficient"]] <- 46.102
df_mxstate[[16,"coefficient"]] <- 83.304
df_mxstate[[21,"coefficient"]] <- 24.126
df_mxstate[[22,"coefficient"]] <- 40.39
df_mxstate[[24,"coefficient"]] <- -0.503
df_mxstate[[30,"coefficient"]] <- 7.905

df_mxstate$value <- df_mxstate$coefficient

mxstate_choropleth(df_mxstate,
                   zoom = subset(df_mxstate, state_name %in% c("Guerrero", "Hidalgo", "Michoacán", "Puebla", "Querétaro", "San Luis Potosí", "Veracruz"))$region,
                   num_colors = 9,
                   title = "Impact on raising living standard subject to States")
```
```{r}
investments<- read.dta13('investments_data.dta')
```